Luminance constancy under fixed geometry

### 2018-04-04 Draft3/draft3.tex
Today’s editing

AMA \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
is a task specific Bayesian method for dimensionality reduction.
When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
These receptive fields have the property that the  expected estimation cost is minimized when their responses are optimally decoded.

More concretely, let us assume that there are $N_{\nu}$ possible values of the target LRV levels ($\{Y_k: k\in[1,N_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$. Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$. Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{Y}_k$) of the target object in each stimulus $s_{kl}$. The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
. With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(Y_{kl},\hat{Y}_{kl})$. Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $Y_k$. Thus,
\begin{align}
{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
\label{eq:fopt}
\end{align}

>>>>

AMA 
is a task specific Bayesian method for dimensionality reduction.
When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
Given a set of linear receptive fields and an explicit cost function, it is possible to determine the minimum-expected-cost estimator that maps responses to stimulus labels given the training set and the 
assumption that all images in the training set are equally likely.
Moreover, the corresponding expected estimation cost may be explicitly computed.
AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
Here we used squared error as the cost function and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e. Poisson-like noise with a fano factor of 1.3).
Details of how AMA learns filters and the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.

% VIJAY make this work
%Let a set of linear receptive fields be represented by the matrix $\textbf{f} = [\textbf{f_1} \hdots \textbf{f_N}]$, where each $\textbf{f_q}$ is a column vector providing the weights defining a single filter's receptive field.
%Once we have a set of receptive fields and a labelled training set, we can find the decoder that minimizes the expected estimation cost on the assumption that all images in the training set are equally likely to occur.
%
%The learning goal is to find a set of receptive fields ${\textbf{f}}^{\rm opt}$ that have the following property.
%Represent a set of linear receptive fields by a matrix 
%Assume that there are $n_{\nu}$ possible values of the target LRV levels ($\{y_k: k\in[1,n_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$. Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$. Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{y}_k$) of the target object in each stimulus $s_{kl}$. The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
%. With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(y_{kl},\hat{y}_{kl})$. Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $y_k$. Thus,
%\begin{align}
%{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
%\label{eq:fopt}
%\end{align}
